What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2024-11-03 manuscript.Rmd
small edits to get it to knit right

  affiliation:
  - id: '4'
    institution: Cognitive Science Department, Vassar College
  - id: '2'
    institution: Department of Cognitive & Information Science, University of California,
      Merced
  - id: '1'
    institution: Psychology Department, Macalester College
  - id: '3'
    institution: Department of Communication Sciences and Disorders, MGH Institute of Health Professions

>>>>

affiliation:
  - id: '1'
    institution: Psychology Department, Macalester College
  - id: '2'
    institution: Department of Cognitive & Information Science, University of California,
      Merced
  - id: '3'
    institution: Department of Communication Sciences and Disorders, MGH Institute of Health Professions
  - id: '4'
    institution: Cognitive Science Department, Vassar College
